WSClean: an implementation of a fast, generic wide-field imager for radio astronomy

### 2014-03-29 articles/2014/Article-WSClean/wsclean.tex
Adding Luke as coauthor, correcting Emil's affiliation

\author[A.~R.~Offringa et al.]{A.~R.~Offringa$^{1,2}$\thanks{E-mail: \url{andre.offringa@anu.edu.au}},
B.~McKinley\ANU$^,$\CAASTRO,
N.~Hurley-Walker\Curtin,
F.~H.~Briggs$^{1,2}$,
R.~B.~Wayth\Curtin$^,$\CAASTRO, \newauthor
D.~L.~Kaplan\UWisc,
M.~E.~Bell\USydney$^,$\CAASTRO,
L.~Feng\MIT,
A.~R.~Neben\MIT,
J.~D.~Hughes\ANU, 
J.~Rhee\ANU, \newauthor
T.~Murphy\USydney$^,$\CAASTRO,
R.~Bhat\Curtin,
G.~Bernardi\SKASA,
J.~D.~Bowman\ASU,
R.~J.~Cappallo\Haystack,
B.~E.~Corey\Haystack, \newauthor
A.~A.~Deshpande\RRI, 
D.~Emrich\Curtin,
A.~Ewall-Wice\MIT,
B.~M.~Gaensler\USydney$^,$\CAASTRO,
R.~Goeke\MIT, \newauthor
L.~J.~Greenhill\CfA, 
B.~J.~Hazelton\UW, 
J.~N.~Hewitt\MIT,
M.~Johnston-Hollitt\Victoria,
D.~C.~Jacobs\ASU, \newauthor
J.~C.~Kasper\UMichigan$^,$\CfA,
E.~Kratzenberg\Haystack, 
E.~Lenc\USydney,
C.~J.~Lonsdale\Haystack,
M.~J.~Lynch\Curtin,
S.~R.~McWhirter\Haystack, \newauthor
D.~A.~Mitchell\CASS$^,$\CAASTRO,
M.~F.~Morales\UW, 
E.~Morgan\MIT,
N.~Kudryavtseva\Curtin,
D.~Oberoi\Tata, \newauthor
S.~M.~Ord\Curtin$^,$\CAASTRO,
P.~Procopio\UMelbourne,
T.~Prabu\RRI,
J.~Riding\UMelbourne, 
A.~E.~E.~Rogers\Haystack,
D.~A.~Roshi\NRAO, \newauthor %\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.},
N.~Udaya~Shankar\RRI,
K.~S.~Srivani\RRI,
R.~Subrahmanyan\RRI$^,$\CAASTRO,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
M.~Waterson\Curtin$^,$\ANU, \newauthor
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin,
C.~L.~Williams\MIT
\\
\ANU{}Research School of Astronomy and Astrophysics, Australian National University, Canberra, ACT 2611, Australia \\
\CAASTRO{}ARC Centre of Excellence for All-sky Astrophysics (CAASTRO), Australian National University, Canberra, ACT 2611, Australia \\
\Curtin{}International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
\UWisc{}Department of Physics, University of Wisconsin--Milwaukee, Milwaukee, WI 53201, USA\\
\USydney{}Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
\MIT{}Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA\\
\SKASA{}Square Kilometre Array South Africa (SKA SA), Cape Town 7405, South Africa\\
\ASU{}School of Earth and Space Exploration, Arizona State University, Tempe, AZ 85287, USA\\
\Haystack{}MIT Haystack Observatory, Westford, MA 01886, USA\\
\RRI{}Raman Research Institute, Bangalore 560080, India\\
\CfA{}Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA\\
\UW{}Department of Physics, University of Washington, Seattle, WA 98195, USA\\
\Victoria{}School of Chemical \& Physical Sciences, Victoria University of Wellington, Wellington 6140, New Zealand\\
\CASS{}CSIRO Astronomy and Space Science, Marsfield, NSW 2122, Australia\\
\Tata{}National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India\\
\UMelbourne{}School of Physics, The University of Melbourne, Parkville, VIC 3010, Australia\\
\NRAO{}National Radio Astronomy Observatory, Charlottesville and Greenbank, USA\\
}

>>>>

\author[A.~R.~Offringa et al.]{A.~R.~Offringa$^{1,2}$\thanks{E-mail: \url{andre.offringa@anu.edu.au}},
B.~McKinley\ANU$^,$\CAASTRO,
N.~Hurley-Walker\Curtin,
F.~H.~Briggs$^{1,2}$,
R.~B.~Wayth\Curtin$^,$\CAASTRO, \newauthor
D.~L.~Kaplan\UWisc,
M.~E.~Bell\USydney$^,$\CAASTRO,
L.~Feng\MIT,
A.~R.~Neben\MIT,
J.~D.~Hughes\ANU, 
J.~Rhee\ANU, \newauthor
T.~Murphy\USydney$^,$\CAASTRO,
N.~D.~R.~Bhat\Curtin,
G.~Bernardi\SKASA,
J.~D.~Bowman\ASU,
R.~J.~Cappallo\Haystack,
B.~E.~Corey\Haystack, \newauthor
A.~A.~Deshpande\RRI, 
D.~Emrich\Curtin,
A.~Ewall-Wice\MIT,
B.~M.~Gaensler\USydney$^,$\CAASTRO,
R.~Goeke\MIT, \newauthor
L.~J.~Greenhill\CfA, 
B.~J.~Hazelton\UW, 
J.~N.~Hewitt\MIT,
L.~Hindson\Victoria,
M.~Johnston-Hollitt\Victoria, \newauthor
D.~C.~Jacobs\ASU,
J.~C.~Kasper\UMichigan$^,$\CfA,
E.~Kratzenberg\Haystack, 
E.~Lenc\USydney$^,$\CAASTRO,
C.~J.~Lonsdale\Haystack,
M.~J.~Lynch\Curtin, \newauthor
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO,
M.~F.~Morales\UW, 
E.~Morgan\MIT,
N.~Kudryavtseva\Curtin, \newauthor
D.~Oberoi\Tata,
S.~M.~Ord\Curtin$^,$\CAASTRO,
P.~Procopio\UMelbourne,
T.~Prabu\RRI,
J.~Riding\UMelbourne, 
A.~E.~E.~Rogers\Haystack, \newauthor
D.~A.~Roshi\NRAO, %\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.},
N.~Udaya~Shankar\RRI,
K.~S.~Srivani\RRI,
R.~Subrahmanyan\RRI$^,$\CAASTRO,
S.~J.~Tingay\Curtin$^,$\CAASTRO, \newauthor
M.~Waterson\Curtin$^,$\ANU,
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin,
C.~L.~Williams\MIT
\\
\ANU{}Research School of Astronomy and Astrophysics, Australian National University, Canberra, ACT 2611, Australia \\
\CAASTRO{}ARC Centre of Excellence for All-sky Astrophysics (CAASTRO), Australian National University, Canberra, ACT 2611, Australia \\
\Curtin{}International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
\UWisc{}Department of Physics, University of Wisconsin--Milwaukee, Milwaukee, WI 53201, USA\\
\USydney{}Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
\MIT{}Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA\\
\SKASA{}Square Kilometre Array South Africa (SKA SA), Cape Town 7405, South Africa\\
\ASU{}School of Earth and Space Exploration, Arizona State University, Tempe, AZ 85287, USA\\
\Haystack{}MIT Haystack Observatory, Westford, MA 01886, USA\\
\RRI{}Raman Research Institute, Bangalore 560080, India\\
\CfA{}Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA\\
\UW{}Department of Physics, University of Washington, Seattle, WA 98195, USA\\
\Victoria{}School of Chemical \& Physical Sciences, Victoria University of Wellington, Wellington 6140, New Zealand\\
\CASS{}CSIRO Astronomy and Space Science, Marsfield, NSW 2122, Australia\\
\Tata{}National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India\\
\UMelbourne{}School of Physics, The University of Melbourne, Parkville, VIC 3010, Australia\\
\NRAO{}National Radio Astronomy Observatory, Charlottesville and Greenbank, USA\\
}
